Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-11 paper/Draft.tex
started NLP task.Notebook importing sample 100 NYT news articles.

	First,  all three forecast series easily reject the unbiasedness test at the significance level of $1\%$. There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecasters(2.2 versus 0.12) for headline CPI.

	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of $1\%$. For headline CPI inflation, for instance, one percentage point inflation forecast corresponds to 0.3 percentage points of the forecast errors one year later. Thus test 2 in Table \ref{NullTestTable} easily rejects the second hypothesis test of FIRE that past information does not predict future forecast errors.

@@

    The second noticeable result lies in the constant regressions reported in the first column of each sub panel in Table \ref{WeakRevEfficiency}. It implies that households constantly lower their mean forecasts as well as uncertainty from month to month, while professional forecasts do not behave in such a way. In particular, the constant regression of change in mean forecast for SCE gives an estimated coefficient of -0.05 which is significant in the $5\%$ level. Individual households' 1-year-ahead inflation expectations keep being downward adjusted each month compared to their previous answer. What is more interesting is that their uncertainty about 1-year-ahead inflation also decrease each month.  The size of downward adjustment is  $-1.39$ unit and statistically significant in the level of $1\%.$. This negative significant constant coefficient remains throughout all auto-regressions, implying it is not driven by time-varying changes.

>>>>

	First,  all three forecast series easily reject the unbiasedness test at the significance level of $0.1\%$. There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecasters(2.2 versus 0.12) for headline CPI.

	Second, the point forecast one year ago predicts the forecast errors for professionals in the significance level of $0.1\%$. For headline CPI inflation, for instance, one percentage point inflation forecast corresponds to 0.3 percentage points of the forecast errors one year later. Thus test 2 in Table \ref{NullTestTable} easily rejects the second hypothesis test of FIRE that past information does not predict future forecast errors.

@@

    The second noticeable result lies in the constant regressions reported in the first column of each sub panel in Table \ref{WeakRevEfficiency}. It implies that households constantly lower their mean forecasts as well as uncertainty from month to month, while professional forecasts do not behave in such a way. In particular, the constant regression of change in mean forecast for SCE gives an estimated coefficient of -0.05 which is significant in the $5\%$ level. Individual households' 1-year-ahead inflation expectations keep being downward adjusted each month compared to their previous answer. What is more interesting is that their uncertainty about 1-year-ahead inflation also decrease each month.  The size of downward adjustment is  $-1.39$ unit and statistically significant in the level of $0.1\%$. This negative significant constant coefficient remains throughout all auto-regressions, implying it is not driven by time-varying changes.
